Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-23 cav2017/cav2017.tex
revised CEGIS with AA figure

\begin{figure}
\centering
{\scriptsize
\hspace*{-1cm}
\begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center},row sep=.8cm, column sep=.2cm] {
   \coordinate (aux1);
   \& \coordinate (aux2);
   \& ;\\
   \&\node[fill=gray!20,align=center] (pre) {{\sc 1. pre-}\\{\sc processing}};
   \& \node[fill=gray!20,align=center] (abstract) {\sc 4. abstraction};
   \& \coordinate (aux); \\ % \node[fill=yellow!20,align=center] (counter) {\sc counterexample};\\
   \& 
   \& \node[fill=gray!20,align=center, minimum width=3cm] (synth) {\sc 2. synthesize};
       %\node[draw=none] (KL) at ([xshift=2.5cm,yshift=-.25cm]synth)  {\sc $\mat{K},\mat{L}$};
       %\node[draw=none] (NKL) at ([xshift=2cm,yshift=1cm]synth)  {\sc $P_a$};
   \& \node[fill=gray!20,align=center, minimum width=4cm] (verify) {\sc 3. verify ($\phi$)};
       %\node[draw=none] (VUNS) at ([xshift=.6cm,yshift=1cm]verify)  {\sc SAT};
       \node[draw=none] (SAT) at ([xshift=2.7cm,yshift=-.3cm]verify)  {\sc SAT};
   \& \node[ellipse, fill=gray!20] (done) {{\sc Done}};\\
   \&
   \& complexnode/.pic={
     \coordinate (auxsynth);
     \node[draw,rectangle,align=center] (KSAT) at ([xshift=0cm]auxsynth.center) {\sc Prog.\\Search};
     \node[draw=none] (SATK) at ([xshift=-0.5cm,yshift=1.5cm]KSAT)  {$\mathcal{J}_K$};
     \node[draw=none] (K) at ([xshift=.4cm,yshift=1.5cm]KSAT)  {$\tilde{\mat{K}}$};
    }
   \& complexnode/.pic={
     \coordinate (AA);
     \node[draw,rectangle,align=center] (AAI) at ([xshift=-1.5cm]AA.center) {\sc AI\\Model};
     \node[draw,rectangle,align=center] (AAC) at ([xshift=1.5cm,yshift=1.5cm]AA.center) {\sc CEGAR};
     \node[draw,rectangle,align=center] (AAV) at ([xshift=1.5cm]AA.center) {\sc AA\\Solver};

     \node[draw=none] (AB) at ([xshift=.4cm,yshift=1.5cm]AAI.center)  {\sc $\mat{A},\mat{B}$\\$\phi$};     
     \node[draw=none] (MA) at ([yshift=.2cm]AA.center)  {$\mathcal{A}_t$};     
     \node[draw=none] (MB) at ([yshift=-.3cm]AA.center)  {$\mathcal{B}_{tp},\mathcal{B}_{tn}$}; 
     \node[draw=none] (XT) at ([xshift=0.3cm,yshift=0.5cm]AAC.center)  {\sl $\hat{X}_r^\#$};  
     \node[draw=none] (XT2) at ([xshift=0.3cm,yshift=0.8cm]AAV.center)  {\sl $\hat{X}^\#$};  
     %\draw [->,line width=1pt] ([xshift=-0.1cm,yshift=2cm]AA.center) arc[x radius=0.7cm, y radius =.7cm, start angle=-250, end angle=60];
    }\\
   \&
   \& complexnode/.pic={
     \coordinate (UNSAT);
     \coordinate (KUNSAT)  at ([xshift=0cm]UNSAT.center);
     \node[draw=none] (UNSATB) at ([xshift=1.6cm,yshift=.3cm]UNSAT)  {\sc UNSAT};
  }
  \& \& \coordinate (FAIL);\\
  };
  \path
    (pre.east) edge (abstract.west)
    (abstract.south) edge (synth.north)
    %([yshift=2em]synth.east) edge node {Candidate} ([yshift=2em]verif.west)
    %([yshift=-2em]verif.west) edge node {New input} ([yshift=-2em]synth.east)
    %([yshift=2em]synth.east) edge node[xshift=-0.7em] {Candidate} ([yshift=2em]verif.west)
    %([yshift=-2em]verif.west) edge node[xshift=-0.7em] {New input} ([yshift=-2em]synth.east)
    ([yshift=1em]synth.east) edge node {$\mat{K}$} ([yshift=1em]verify.west)
    ([yshift=-1em]verify.west) edge node {$P_a$} ([yshift=-1em]synth.east)
    (aux) edge (abstract.east) 
    (verify.east) edge (done.west);
  \path
    ([xshift=+.6cm]KSAT.north) edge ([xshift=0.6cm]synth.south) 
    ([xshift=-.6cm]synth.south) edge ([xshift=-.6cm]KSAT.north)
    ([xshift=-4.9cm]verify.south) edge (AAI.north)
    (AAI.east) edge (AAV.west)
    (AAV.north) edge (AAC.south)
    (AAC.north) edge ([xshift=4.9cm]verify.south)
    (AAC.west) edge (AB.west)
    %(verify.north) edge (counter.south)
    %(counter.west) edge (abstract.east)
    %(counter.south west) edge (synth.north east)
    (FAIL.north) edge (done.south);
   \path[-] 
     (KSAT.south) edge (KUNSAT.north)
     (KUNSAT.east) edge (FAIL.west)
     (verify.north) edge node {$\phi (\mat{K},k)$} (aux);
\end{tikzpicture}
}
\caption{CEGIS with abstraction refinement}
\label{fig:CEGARIS} 
\end{figure}

>>>>

\begin{figure}
\centering
{\scriptsize
\hspace*{-1cm}
\begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center},row sep=.8cm, column sep=.2cm] {
   \coordinate (aux1);
   \& \coordinate (aux2);
   \& ;\\
   \&\node[fill=gray!20,align=center] (pre) {{\sc 1. pre-}\\{\sc processing}};
   \& \node[fill=gray!20,align=center] (abstract) {\sc 4. abstract};
   \& \coordinate (aux); \\ % \node[fill=yellow!20,align=center] (counter) {\sc counterexample};\\
   \& 
   \& \node[fill=gray!20,align=center, minimum width=3cm] (synth) {\sc 2. synthesize};
       %\node[draw=none] (KL) at ([xshift=2.5cm,yshift=-.25cm]synth)  {\sc $\mat{K},\mat{L}$};
       %\node[draw=none] (NKL) at ([xshift=2cm,yshift=1cm]synth)  {\sc $P_a$};
   \& \node[fill=gray!20,align=center, minimum width=4cm] (verify) {\sc 3. verify ($\phi$)};
       %\node[draw=none] (VUNS) at ([xshift=.6cm,yshift=1cm]verify)  {\sc SAT};
       \node[draw=none] (SAT) at ([xshift=2.7cm,yshift=-.3cm]verify)  {\sc SAT};
   \& \node[ellipse, fill=gray!20] (done) {{\sc Done}};\\
   \&
   \& complexnode/.pic={
     \coordinate (auxsynth);
     \node[draw,rectangle,align=center] (KSAT) at ([xshift=0cm]auxsynth.center) {\sc Prog.\\Search};
     \node[draw=none] (SATK) at ([xshift=-0.5cm,yshift=1.5cm]KSAT)  {$\mathcal{J}_K$};
     \node[draw=none] (K) at ([xshift=.4cm,yshift=1.5cm]KSAT)  {$\tilde{\mat{K}}$};
    }
   \& complexnode/.pic={
     \coordinate (AA);
     \node[draw,rectangle,align=center] (AAI) at ([xshift=-1.5cm]AA.center) {\sc Abstract};
     \node[draw,rectangle,align=center] (AAC) at ([xshift=1.5cm,yshift=1.5cm]AA.center) {Abstraction \\ Verifier};
     \node[draw,rectangle,align=center] (AAV) at ([xshift=1.5cm]AA.center) {\sc AA\\Solver};

     %\node[draw=none] (AB) at ([xshift=.4cm,yshift=1.5cm]AAI.center)  {\sc $\mat{A},\mat{B}$\\$\phi$};     
     \node[draw=none] (MA) at ([yshift=.2cm]AA.center)  {$\mathcal{A}_t$};     
     \node[draw=none] (MB) at ([yshift=-.3cm]AA.center)  {$\mathcal{B}_{tp},\mathcal{B}_{tn}$}; 
     \node[draw=none] (XT) at ([xshift=0.3cm,yshift=0.5cm]AAC.center)  {\sl $\hat{X}_r^\#$};  
     \node[draw=none] (XT2) at ([xshift=0.3cm,yshift=0.8cm]AAV.center)  {\sl $\hat{X}^\#$};  
     %\draw [->,line width=1pt] ([xshift=-0.1cm,yshift=2cm]AA.center) arc[x radius=0.7cm, y radius =.7cm, start angle=-250, end angle=60];
    }\\
   \&
   \& complexnode/.pic={
     \coordinate (UNSAT);
     \coordinate (KUNSAT)  at ([xshift=0cm]UNSAT.center);
     \node[draw=none] (UNSATB) at ([xshift=1.6cm,yshift=.3cm]UNSAT)  {\sc UNSAT};
  }
  \& \& \coordinate (FAIL);\\
  };
  \path
    (pre.east) edge (abstract.west)
    (abstract.south) edge (synth.north)
    %([yshift=2em]synth.east) edge node {Candidate} ([yshift=2em]verif.west)
    %([yshift=-2em]verif.west) edge node {New input} ([yshift=-2em]synth.east)
    %([yshift=2em]synth.east) edge node[xshift=-0.7em] {Candidate} ([yshift=2em]verif.west)
    %([yshift=-2em]verif.west) edge node[xshift=-0.7em] {New input} ([yshift=-2em]synth.east)
    ([yshift=1em]synth.east) edge node {$\mat{K}$} ([yshift=1em]verify.west)
    ([yshift=-1em]verify.west) edge node {$P_a$} ([yshift=-1em]synth.east)
    (aux) edge (abstract.east) 
    (verify.east) edge (done.west);
  \path
    ([xshift=+.6cm]KSAT.north) edge ([xshift=0.6cm]synth.south) 
    ([xshift=-.6cm]synth.south) edge ([xshift=-.6cm]KSAT.north)
    (AAC) edge[bend right] node[align=center] {$k$} (AAI.north)
    ([xshift=-4.9cm]verify.south) edge node[align=center] {$\mat{A},\mat{B}$\\$\phi$} (AAI.north)
    (AAI.east) edge (AAV.west)
    (AAV.north) edge (AAC.south)
    (AAC.north) edge ([xshift=4.9cm]verify.south)
    %(AAC.west) edge (AB.west)
    %(verify.north) edge (counter.south)
    %(counter.west) edge (abstract.east)
    %(counter.south west) edge (synth.north east)
    (FAIL.north) edge (done.south);
   \path[-] 
     (KSAT.south) edge (KUNSAT.north)
     (KUNSAT.east) edge (FAIL.west)
     (verify.north) edge node {$\phi (\mat{K},k)$} (aux);
\end{tikzpicture}
}
\caption{CEGIS with abstraction refinement}
\label{fig:CEGARIS} 
\end{figure}
